---
title: "Lab 6"
author: "An Bui"
date: "07 November 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### 1. Set up.
```{r set up code, include = FALSE}
library(tidyverse)

hp_data <- read_csv("harry_potter_aggression_full.csv")
```

Save .rmd to github to save this version stored somewhere. Go through a 3 step process:  
**1. Stage** Select files
**2. Commit** Select commit. _Always add a message_ to know what changed in that version.  
**3. Push** Push to github.  

In R, nothing will show up to commit unless you've changed something in your file.

On github:  
- click on the file to see what the version looks like

#### 2. Basic wrangling and make a graph.
Compare Harry and Draco's aggression rates.

```{r basic graph}
# create new data from from hp_data
hp_graph <- hp_data %>% 
  # filter rows by Harry and Draco Malfoy
  filter(Name == "Harry" | Name == "Draco Malfoy") %>% 
  # select columns desired
  select(Name, book, agg.per.mention) %>% 
  
  # pipe into ggplot to graph, don't have to call the data frame because it knows to use the one from the pipe
  ggplot(aes(x = book, y = agg.per.mention)) +
  # make a column graph - default is to stack, make the fill based on Name, position = "dodge" makes it cluster by book
  geom_col(aes(fill = Name), position = "dodge") +
  # make books go on y-axis
  coord_flip() +
  # theme things
  theme_bw()

hp_graph
```
















